The National Eutrophication Survey: lake characteristics and historical nutrient concentrations

### 2017-12-04 08_manuscript/post_response.tex
add acknowledgements

\begin{acknowledgements}

\end{acknowledgements}

>>>>

\begin{acknowledgements}
  This work was developed as part of the Reproducible Quantitative Methods course (https://cbahlai.github.io/rqm-template/) led by Dr. Christie Bahlai which was funded by the Mozilla Foundation, the Leona M. and Harry B. Helmsley Charitable Trust, the Michigan State University Program in Ecology and Evolutionary Biology, the BEACON Center for Evolution in Action, and the Kellogg Biological Station Long Term Ecological Research Site (NSF-DEB \#1027253).
\end{acknowledgements}
